---
title: "Map"
author: "Patrick Spauster"
date: "3/18/2022"
output: html_document
---

```{r}

library(tidyverse)
library(shiny)    # for shiny apps
library(leaflet)  # renderLeaflet function
library(tigris)
library(sf)

```


#shiny to create map that changes over time

library(shiny)    # for shiny apps
library(leaflet)  # renderLeaflet function
library(spData)   # loads the world dataset 
ui = fluidPage(
  sliderInput(inputId = "life", "Life expectancy", 49, 84, value = 80),
      leafletOutput(outputId = "map")
  )
server = function(input, output) {
  output$map = renderLeaflet({
    leaflet() %>% 
      # addProviderTiles("OpenStreetMap.BlackAndWhite") %>%
      addPolygons(data = world[world$lifeExp < input$life, ])})
}
shinyApp(ui, server)

https://geocompr.robinlovelace.net/adv-map.html


```{r}

library(spData)   # loads the world dataset 
library(rjson)

spdata::world()

world <- world



ui = fluidPage(
  sliderInput(inputId = "life", "Life expectancy", 49, 84, value = 80),
      leafletOutput(outputId = "map")
  )
server = function(input, output) {
  output$map = renderLeaflet({
    leaflet() %>% 
      # addProviderTiles("OpenStreetMap.BlackAndWhite") %>%
      addPolygons(data = world[world$lifeExp < input$life, ])})
}
shinyApp(ui, server)



```


# Shapefile
```{r}
states_code_list <- state.abb

county_shapes <- counties(state = states_code_list, cb = T)%>% 
  mutate(centroid = st_centroid(geometry)) %>% 
  st_transform(crs = 4326)

```

# get USA county COVID data from github and merge to shapes

```{r}
covid_daily_county_nyt <- read_csv("https://raw.githubusercontent.com/nytimes/covid-19-data/master/us-counties.csv")

covid_shapes <- left_join(covid_daily_county_nyt, county_shapes, by = c("fips" = "GEOID")) 

yesterday <- covid_shapes %>% 
  filter(date == "2022-03-19") %>%
    mutate(lat = unlist(map(.$centroid,2)),
           long = unlist(map(.$centroid,1))) %>% 
  as.data.frame()

```

test map for today
```{r}

leaflet() %>% 
  addTiles() %>% 
  #addProviderTiles(providers$CartoDB.Positron) %>%
  addPolygons(data = county_shapes) %>% 
  addCircles(
    lng = yesterday$long, lat = yesterday$lat, 
    radius = yesterday$cases/1000
  )


```



#create shiny leaflet map

```{r}


ui = fluidPage(
  sliderInput(inputId = "date", "Date", min = as.Date("2020-01-21"), max = as.Date(covid_daily_county_nyt$date[length(covid_daily_county_nyt$date)]),
              value = as.Date(covid_daily_county_nyt$date[length(covid_daily_county_nyt$date)])),
      leafletOutput(outputId = "map")
  )
server = function(input, output) {
  output$map = renderLeaflet({
    leaflet() %>% 
      # addProviderTiles("OpenStreetMap.BlackAndWhite") %>%
      addPolygons(data = world[world$lifeExp < input$life, ])})
}
shinyApp(ui, server)


```



